---
title: "filter by country"
output: html_document
---

# filtering


```{r}
library(dplyr)
library(plyr)

personal = read.csv("personal_total.csv")
skills = read.csv("skills_total.csv")
job = read.csv("job_total.csv")


job = job %>%
  dplyr::rename(year = Year)

job = job %>%  relocate(year)

total = cbind(personal, skills, job)
total = total[, -total$year]

```


**filter country**
country < 3000

```{r}

country = as.data.frame(table(total["Country"]))
country = country[country$Freq > 3000, ]


country_filtered = total %>% filter(Country %in%
                                      as.character(factor(country$Var1)))
write.csv(country_filtered, "country_filtered.csv", row.names = FALSE)
```

**filter salary**
```{r}
salary_filtered = country_filtered %>% 
  filter(!is.na(Salary)) %>%
  filter(Salary != 0)
write.csv(salary_filtered , "salary_filtered.csv", row.names = FALSE)
```


```{r}

as.data.frame(table(salary_filtered["Ethnicity"]))
as.data.frame(table(salary_filtered["EdLevel"]))
as.data.frame(table(salary_filtered["Country"]))
```




